Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-05 paper/paper.tex
fix running example solution
fix running example
revised intro

Modern implementations of embedded control have proliferated with the
availability of low cost devices that can perform simple tasks for
linear control, spanning many areas such as environmental control and
robotic manipulations. The downside to this approach is that in order
to achieve low prices, devices are often limited in their
capabilities, be it a low number of gates in an FPGA or short word
lengths for microcontrollers. In most cases a floating point
implementation is not feasible and the system can benefit from the
added resolution of a fixed point representation. The ubiquity of
these devices requires that they have a robust design that ensures the
correct behaviour in a number of environments.  For this reason it is
necessary to provide design tools that formally verify the correctness
of the digital controller and in particular we explore the automatic
synthesis of these controllers which reduces the deveopment cost and
design time for a number of models.  \cdsay{the last sentence
  is misleading given that synthesis is not a special case of
  verification, but taking it one step forward.}

We are interested in the stability of hybrid closed-loop systems,
i.e., embedded controllers along with a model of their physical
environment, the plant, as shown in Fig.~\ref{fig:closed-system}.
\cdsay{in the next paragraph we say that our primary interest is
  evaluating digital effects in addition to stability, which
  contradicts the previous sentence, where we only mention stability.}
Due to the complexity of such systems, we focus on linear models with
known configurations to perform parametric synthesis of the controller
dynamics.

@@

For this particular example, the actual implementation of $C(z)$ using
\param{3}{16} implementation format can be represented by the following
z-expression:

\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2 - 4.1529998779296875z + 1.89599609375}{z^2 - 1.843994140625z + 0.8495941162109375},$
}
\end{equation}

>>>>

Modern implementations of embedded control have proliferated with the
availability of low cost devices that can perform simple tasks for
linear control, spanning many areas such as environmental control and
robotic manipulations. The downside to this approach is that in order
to achieve low prices, devices are often limited in their
capabilities, be it a low number of gates in an FPGA or short word
lengths for microcontrollers. In most cases a floating point
implementation is not feasible and the system can benefit from the
added resolution of a fixed point representation. The ubiquity of
these devices requires that they have a robust design that ensures the
correct behaviour in a number of environments.  % For this reason it is
% necessary to provide design tools that formally verify the correctness
% of the digital controller.

\cdsay{Mention that the resulting systems are also expected to have certain properties, 
e.g. stability, which makes it even more difficult to synthesise them?}

In this paper, we explore the automatic synthesis of 
{\em correct-by-construction} controllers, which 
reduces the deveopment cost and design time for a number of models.  
In particular, we are interested in synthesising controllers 
for {\em hybrid closed-loop systems}, i.e., embedded controllers along with a model of their
physical environment, the plant, as shown in
Fig.~\ref{fig:closed-system}, that are {\em stable}.  Due to the complexity
of such systems, we focus on linear models with known configurations
to perform parametric synthesis of the controller dynamics.

@@

For this particular example, the actual implementation of $C(z)$ using
\param{20}{20} implementation format can be represented by the following
z-expression:

\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{4.00888156890869140625z^2{-}0.00041961669921875z
-0.000213623046875}{-0.003753662109375z^2{+}7.37355804443359375z-7.2847900390625},$
}
\end{equation}
